---
title: "Lab 07 - Modelling course evaluations"
author: "INSERT NAME HERE"
date: "`r Sys.Date()`"
output: html_document
---

### Packages and Data

```{r load-packages, message=FALSE, echo=TRUE}
library(tidyverse)
library(tidymodels)

```


```{r read-data}
evals<-read.csv("data/evals.csv", row.names=1)
```


# Exercise 1: Exploratory Data Analysis

1.  Visualize the distribution of `score` in the dataframe `evals`.

```{r viz-score}
ggplot(data = evals, mapping = aes(x = score)) +
  geom_histogram()
  

summarise(evals, mean = mean(score, na.rm=TRUE),
          median = median(score, na.rm=TRUE), 
          IQR = IQR(score, na.rm=TRUE),
          sd = sd(score, na.rm=TRUE),
          minimum = min(score, na.rm=TRUE),
          maximum = max(score, na.rm=TRUE))
```

*It is left skew, median is 4.3, mean is 4.2 and the lowest rating is 2.3. This is what I expected as when asked to give ratings people tend to rate things higher than a strictly mathematical outlook would suggest. E.g a 5/10 meal sounds not that nice when really it means it is completely average. This means most ratings tend to have a average higher than the middle score.*

2.  Visualize and describe the relationship between `score` and `bty_avg` using `geom_point()` to represent the data. 

```{r scatterplot}
ggplot(data = evals, mapping = aes(y = score, x = bty_avg)) +
  geom_point()

ggplot(data = evals, mapping = aes(y = score, x = bty_avg)) +
  geom_jitter()
```

*The first scatterplot doesn't communicate that some of the entries have multiple data points at exactly the same point. The jitter plot shows this by offsetting them all slightly.*

# Exercise 2: Simple Linear regression with a numerical predictor

1. Fit a linear model called `score_bty_fit` to predict average professor evaluation `score` from average beauty rating (`bty_avg`). Print the regression output using `tidy()`.

```{r fit-score_bty_fit}
score_bty_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(score ~ bty_avg, data = evals)
```

```{r tidy-score_bty_fit}
tidy(score_bty_fit)
```

*score-hat = 3.88 + 0.067bty_avg*

2. Plot the data again using `geom_jitter()`, and add the regression line.

```{r viz-score_bty_fit,eval=FALSE}
ggplot(data = evals, mapping = aes(y = score, x = bty_avg)) +
  geom_jitter() +
  geom_smooth(method = "lm", se = FALSE)
```

3. Interpret the slope of the linear model in context of the data.

*the more attractive professors receive slightly better feedback*

4. Interpret the intercept of the linear model in context of the data. Comment on whether or not the intercept makes sense in this context.

*a professor who received an attractiveness rating of zero would still score 3.88, yes this makes sense.*

5. Determine the $R^2$ of the model and interpret it in the context of the data.

```{r R2, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
glance(score_bty_fit)$r.squared
```

*My model describes about 3 percent of the data*

6. Make a plot of residuals vs. predicted values for the model above.

```{r viz-score_bty_fit-diagnostic, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_aug <- augment(score_bty_fit$fit)

ggplot(data = score_bty_aug) +
  geom_jitter(mapping = aes(x = .fitted, y = .resid)) +
  geom_hline(yintercept = 0, linetype = "dashed")
```

*no as the residuals are quite large*

# Exercise 3: Simple Linear regression with a categorical predictor

0. Look at the variable rank, and determine the frequency of each category level.

```{r}
evals %>%
  group_by(rank) %>%
  count()
```

1. Fit a new linear model called `score_rank_fit` to predict average professor evaluation `score` based on `rank` of the professor.

```{r fit-score_rank_fit}
# fit model
score_rank_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(score ~ rank, data = evals)


# tidy model output
tidy(score_rank_fit)
```

*If the professor is tenured then they will score on average 0.1452 less. with no tenured rank they will score on average 4.284*
2. Fit a new linear model called `score_gender_fit` to predict average professor evaluation `score` based on `gender` of the professor. 

```{r fit-score_gender_fit}
# fit model
score_gender_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(score ~ gender, data = evals)

# tidy model output
tidy(score_gender_fit)

```

```{r score_gender_intercept}
score_gender_intercept <- tidy(score_gender_fit) %>% 
  filter(term == "(Intercept)") %>%
  select(estimate) %>%
  pull()
```

```{r score_gender_slope}
score_gender_slope <- tidy(score_gender_fit) %>% 
  filter(term == "gendermale") %>%
  select(estimate) %>%
  pull()
```

*Add your narrative here. Use in-line code!*

# Exercise 4: Multiple linear regression

1. Fit a multiple linear regression model, predicting average professor evaluation `score` based on average beauty rating (`bty_avg`) and `gender.`

```{r fit-score_bty_gender_fit}
# fit model

# tidy model output
```

*Add your narrative here.*

```{r eval = FALSE}
ggplot(___) + ...
```

2. What percent of the variability in `score` is explained by the model `score_bty_gender_fit`. 

```{r}
# ...
```


3. What is the equation of the line corresponding to just male professors?

*Add your equation here.*

4. For two professors who received the same beauty rating, which gender tends to have the higher course evaluation score?

*Add your narrative here.*

5. How does the relationship between beauty and evaluation score vary between male and female professors?

*Add your narrative here.*

6. How do the adjusted $R^2$ values of `score_bty_fit` and `score_bty_gender_fit` compare? 

```{r eval=FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
glance(___)$adj.r.squared
glance(___)$adj.r.squared
```

*Add your narrative here.*

7. Compare the slopes of `bty_avg` under the two models (`score_bty_fit` and `score_bty_gender_fit`).

*Add your narrative here.*

# Exercise 5: Interpretation of log-transformed response variables

If you do not know how to use LaTeX, do this exercise with pen and paper.
